---
title: "lobster-report"
format: html
---

# Final Lobster Report

Outline of Instructions:

-   citation of the data

-   brief summary of the abstract (i.e. 1-2 sentences) from the [EDI Portal](https://portal.edirepository.org/nis/mapbrowse?packageid=knb-lter-sbc.77.8)

-   Owner analysis and visualizations (you choose which plots you want to include)

    -   Try adding alternative text to your plots (See [Quarto Documentation](https://quarto.org/docs/authoring/figures.html#alt-text))

    -   Plots can be added either with the data visualization code or with Markdown syntax (calling a saved image) - it’s up to you if you want to include the code or not.

-   Collaborator analysis and visualizations (you choose which plots you want to include)

    -   Try adding alternative text to your plots (See [Quarto Documentation](https://quarto.org/docs/authoring/figures.html#alt-text))

    -   plots can be added either with the data visualization code or with Markdown syntax (calling a saved image) - it’s up to you if you want to include the code or not.

Finally, publish on GitHub pages (from Owner’s repository). Refer back to Chapter 12 for steps on how to publish using GitHub pages.

## Owner analysis
```{r}
# line and point plot
ggplot(data = lobsters_summarize, aes(x = YEAR, y = COUNT)) +
  geom_point(aes(color = SITE)) +
  geom_line(aes(color = SITE))+
  theme(legend.position = "bottom",
          axis.ticks.y = element_blank())
```
This a line graph of the number of total lobsters observed by year. Different color refers to different site of the lobsters. The year ranges from 2012-2022. There is a sharp increasing trend from 2012-2017. 

```{r}
#doged bar plot

ggplot(data = lobster_size_lrg, aes(x = SITE, y = COUNT, fill = SIZE_BIN)) +
    geom_col(position = "dodge")
```
This is a bar graph that shows the amount of small and large sized carapace lobsters. It is interesting that there are more large lobsters at all sites. 


