---
title: "lobster-report"
format: html
---

# Final Lobster Report

Outline of Instructions:

-   citation of the data

-   brief summary of the abstract (i.e. 1-2 sentences) from the [EDI Portal](https://portal.edirepository.org/nis/mapbrowse?packageid=knb-lter-sbc.77.8)

-   Owner analysis and visualizations (you choose which plots you want to include)

    -   Try adding alternative text to your plots (See [Quarto Documentation](https://quarto.org/docs/authoring/figures.html#alt-text))

    -   Plots can be added either with the data visualization code or with Markdown syntax (calling a saved image) - it’s up to you if you want to include the code or not.

-   Collaborator analysis and visualizations (you choose which plots you want to include)

    -   Try adding alternative text to your plots (See [Quarto Documentation](https://quarto.org/docs/authoring/figures.html#alt-text))

    -   plots can be added either with the data visualization code or with Markdown syntax (calling a saved image) - it’s up to you if you want to include the code or not.

Finally, publish on GitHub pages (from Owner’s repository). Refer back to Chapter 12 for steps on how to publish using GitHub pages.

<<<<<<< HEAD
## Collaborator analysis and visualizations

## 1. Line Plot (Total Lobster Commercial Traps by Year and Site)
To include this plot in your Quarto document, you can either generate it inline or save it as an image and include it via Markdown.

```{r}
# Styled line plot for total lobster commercial traps by year and site
lobster_trap_plot <- ggplot(data = lobster_traps_summarize, aes(x = YEAR, y = TOTAL_TRAPS, color = SITE)) +
  geom_line(size = 1.2, linetype = "solid") +  # Adjust line size and type
  geom_point(size = 3) +  # Add larger points
  labs(title = "Total Lobster Commercial Traps by Year and Site",
       x = "Year",
       y = "Total Traps",
       color = "Site") +  # Modify axis, legend, and plot labels
  scale_x_continuous(breaks = seq(min(lobster_traps_summarize$YEAR), max(lobster_traps_summarize$YEAR), by = 1)) +  # Adjust x-axis breaks
  theme_light() +  # Add a clean, light theme
  theme(
    text = element_text(size = 14, family = "Arial"),  # Customize text size and font
    axis.title.y = element_text(margin = margin(r = 10)),  # Add margin to the y-axis title
    panel.grid.major = element_line(color = "gray80", linetype = "dashed"),  # Customize major grid lines
    panel.background = element_rect(fill = "white"),  # Set panel background to white
    plot.background = element_rect(fill = "lightblue", color = NA),  # Set plot background
    legend.position = "bottom",  # Move legend to the bottom
    plot.title = element_text(hjust = 0.5)  # Center the title
  )

# Display the plot
print(lobster_trap_plot)

# Save the plot with alternative text
ggsave(here::here("figs/lobster_trap_plot.png"), plot = lobster_trap_plot, width = 10, height = 6)

```

## 2. Bar Chart (Fishing Pressure)

```{r}
# Bar plot showing high and low fishing pressure by SITE from 2019-2021
fishing_pressure_plot <- ggplot(data = lobster_traps_filtered, aes(x = SITE, fill = FISHING_PRESSURE)) +
  geom_bar(position = "dodge") +
  labs(title = "Fishing Pressure of Lobster Commercial Traps (2019-2021)",
       x = "Site",
       y = "Count of Fishing Pressure",
       fill = "Fishing Pressure") +
  theme_minimal() +  # Apply a minimal theme
  theme(
    text = element_text(size = 12, family = "Arial"),
    plot.title = element_text(hjust = 0.5),
    legend.position = "bottom"
  )

# Display the plot
print(fishing_pressure_plot)

# Save the bar plot with alt text
ggsave(here::here("figs/fishing_pressure_plot.png"), plot = fishing_pressure_plot, width = 10, height = 6)

```

## 3. Histogram (Lobster Traps by Year)

```{r}
# Histogram with customized colors and theme
ggplot(data = lobster_traps, aes(x = TRAPS)) +
  geom_histogram(fill = "steelblue", color = "black", binwidth = 10) +
  facet_wrap(~YEAR) +
  labs(title = "Histogram of Lobster Traps by Year",
       x = "Number of Traps",
       y = "Frequency") +
  theme_minimal()

# Save the histogram plot
ggsave(here::here("figs/lobster_traps_histogram.png"), width = 10, height = 6)

```

## Owner analysis
```{r}
# line and point plot
ggplot(data = lobsters_summarize, aes(x = YEAR, y = COUNT)) +
  geom_point(aes(color = SITE)) +
  geom_line(aes(color = SITE))+
  theme(legend.position = "bottom",
          axis.ticks.y = element_blank())
```
This a line graph of the number of total lobsters observed by year. Different color refers to different site of the lobsters. The year ranges from 2012-2022. There is a sharp increasing trend from 2012-2017. 

```{r}
#doged bar plot

ggplot(data = lobster_size_lrg, aes(x = SITE, y = COUNT, fill = SIZE_BIN)) +
    geom_col(position = "dodge")
```
This is a bar graph that shows the amount of small and large sized carapace lobsters. It is interesting that there are more large lobsters at all sites. 

>>>>>>> 6d27ecfa8822e3dec81181013b15cd3bbd9661c3

